Effect of quality-adjusted production function inputs

### 2015-06-29 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Edits for better documentation and formatting.

  modelsCST <- list()
  # Output elasticities based on cost share theorem
  alphaCST <- 0.3 # Fraction of national accounts spent on capital
  betaCST <- 0.7 # Fraction of national accounts spent on labor
  for (country in countries){
    form <- keep_summands(formulas[[country]][["unadjusted"]], n=-3) # Remove energy
    yVar <- as.name(summands(form, n=1, right=FALSE))
    kVar <- as.name(summands(form, n=1))
    lVar <- as.name(summands(form, n=2))
    tVar <- as.name(summands(form, n=3))
    data <- historicalData[[country]]
    # Cobb-Douglas
    cdModCST <- lm(log(eval(yVar)) - alphaCST*log(eval(kVar)) - betaCST*log(eval(lVar)) ~ eval(tVar), data = data)
    attr(cdModCST, "naturalCoeffs") <- data.frame(lambda=coef(cdModCST)[[2]],
                                                  logscale=coef(cdModCST)[[1]], 
                                                  scale=exp(coef(cdModCST)[[1]]),
                                                  alpha_1=alphaCST,
                                                  alpha_2=betaCST, 
                                                  alpha_3=0)
    cdModCST$formula <- form
    sdata <- subset(data, select=all.vars(form))
    sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
    cdModCST$data <- sdata
    cdModCST$response <- sdata$iGDP 
    modelsCST[[country]][["unadjusted"]][["noE"]][["CD"]] <- cdModCST
    # CES
    cesModCST <- plm(log(eval(yVar) / (alphaCST*eval(kVar)^(-rho_1) + betaCST*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
                     data = historicalData[[country]],
                     params=c(rho_1=0.8))
    names(cesModCST$coefficients) <- c("logscale", "lambda", "rho_1")
    cesModCST$coefficients <- c(coef(cesModCST), c(delta_1=alphaCST, delta=1))
    attr(cesModCST, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCST)
    cesModCST$formula <- form
    cesModCST$data <- sdata
    modelsCST[[country]][["unadjusted"]][["noE"]][["CES"]][["kl"]] <- cesModCST
  }
  # Save cost-share theorem models to disk.
  saveRDS(modelsCST, file=fileNameCST)

@@

  models <- list()
  for(country in countries){
    for (flavor in flavors){
      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term
      fwithE <- formulas[[country]][[flavor]]
      # CD models
      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
      # CES models
      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
                                                                        data = historicalData[[country]], 
                                                                        nest=c(1,2))
      nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
      models[[country]][[flavor]][["withE"]][["CES"]] <- 
        lapply(nestsWithE, function(nest){
          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
        })
    }      
  }
  # Save models to disk.
  saveRDS(models, file=fileName)
}
# Put all the cost-share theorem (CST) coefficients into a data frame
AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){
  # Parse the id to find out whether this is quality-adjusted data, etc.
  id_list <- strsplit(id, split = "[.]")[[1]]
  res <- rbind(list(Country = id_list[[1]], 
                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
                    model=id_list[[4]], 
                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
                    cst=TRUE))
  res <- cbind(res, naturalCoef(modCST))
  # Now calculate the mean squared error (mse) for each model.
  sqResids <- resid(modCST)^2
  mse <- sum(sqResids)/(length(sqResids))
  res <- cbind(res, list(mse=mse))
  return(res)
}) %>% do.call(plyr::rbind.fill, .)

>>>>

  modelsCST <- list()
  # Output elasticities based on cost share theorem
  alphaCST <- 0.3 # Fraction of national accounts spent on capital
  betaCST <- 0.7 # Fraction of national accounts spent on labor
  for (country in countries){
    # Replace with better code later. 
    # Would like to say cdMod(formula, data, fittingParams=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
    # or something like that.
    form <- keep_summands(formulas[[country]][["unadjusted"]], n=-3) # Remove energy
    yVar <- as.name(summands(form, n=1, right=FALSE))
    kVar <- as.name(summands(form, n=1))
    lVar <- as.name(summands(form, n=2))
    tVar <- as.name(summands(form, n=3))
    data <- historicalData[[country]]
    # Cobb-Douglas
    cdModCST <- lm(log(eval(yVar)) - alphaCST*log(eval(kVar)) - betaCST*log(eval(lVar)) ~ eval(tVar), data = data)
    attr(cdModCST, "naturalCoeffs") <- data.frame(lambda=coef(cdModCST)[[2]],
                                                  logscale=coef(cdModCST)[[1]], 
                                                  scale=exp(coef(cdModCST)[[1]]),
                                                  alpha_1=alphaCST,
                                                  alpha_2=betaCST, 
                                                  alpha_3=0)
    cdModCST$formula <- form
    sdata <- subset(data, select=all.vars(form))
    sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
    cdModCST$data <- sdata
    cdModCST$response <- sdata$iGDP 
    modelsCST[[country]][["unadjusted"]][["noE"]][["CD"]] <- cdModCST
    # CES
    cesModCST <- plm(log(eval(yVar) / (alphaCST*eval(kVar)^(-rho_1) + betaCST*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
                     data = historicalData[[country]],
                     params=c(rho_1=0.8))
    names(cesModCST$coefficients) <- c("logscale", "lambda", "rho_1")
    cesModCST$coefficients <- c(coef(cesModCST), c(delta_1=alphaCST, delta=1))
    attr(cesModCST, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCST)
    cesModCST$formula <- form
    cesModCST$data <- sdata
    modelsCST[[country]][["unadjusted"]][["noE"]][["CES"]][["kl"]] <- cesModCST
  }
  # Save cost-share theorem models to disk.
  saveRDS(modelsCST, file=fileNameCST)

@@

  models <- list()
  for(country in countries){
    for (flavor in flavors){
      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term (3rd term on RHS)
      fwithE <- formulas[[country]][[flavor]]
      # CD models
      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
      # CES models
      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
                                                                        data = historicalData[[country]], 
                                                                        nest=c(1,2))
      nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
      models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
        })
    }      
  }
  # Save models to disk.
  saveRDS(models, file=fileName)
}
# Put all the cost-share theorem (CST) coefficients into a data frame
AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){
  # Parse the id to find out whether this is quality-adjusted data, etc.
  id_list <- strsplit(id, split = "[.]")[[1]]
  res <- rbind(list(Country = id_list[[1]], 
                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
                    model=id_list[[4]], 
                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
                    cst=TRUE))
  res <- cbind(res, naturalCoef(modCST))
  # Now calculate the mean squared error (mse) for each model.
  sqResids <- resid(modCST)^2
  mse <- sum(sqResids)/(length(sqResids))
  res <- cbind(res, list(mse=mse))
  return(res)
}) %>% do.call(plyr::rbind.fill, .)
